---
title: "in_class activity,Sep19, 615"
format: html
editor: visual
---

# Description

The `DNase` data frame has 176 rows and 3 columns of data obtained during development of an ELISA assay for the recombinant protein DNase in rat serum.

This dataset was originally part of package [**nlme**](https://cran.r-project.org/package=nlme), and that has methods (including for `[`, `as.data.frame`, `plot` and `print`) for its grouped-data classes.

# Format

Run: an ordered factor with levels `10` \< ... \< `3` indicating the assay run.

Conc: a numeric vector giving the known concentration of the protein.

Density: a numeric vector giving the measured optical density (dimensionless) in the assay. Duplicate optical density measurements were obtained.

# Details

An object of class `c("nfnGroupedData", "nfGroupedData", "groupedData", "data.frame")` containing the following columns:

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(ggplot2)
library(lorem)
```

```{r}
# Load dataset
data(DNase, package = "datasets")

# Quick look
head(DNase)

# Plot density vs concentration
library(ggplot2)

ggplot(DNase, aes(x = conc, y = density, color = Run)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  labs(title = "Optical Density vs Concentration in DNase Experiment",
       x = "DNA Concentration",
       y = "Optical Density") +
  theme_minimal()
```
